NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision_Letter.Rmd
Update Revision Letter

[address frist sentence] We deleted the reference to Grass et al. because referencing it fully would have exceeded the word limit for the abstract.

@@

\RC{Page 3. 
How is NFC related to other constructs like neuroticism, self-esteem, and locus of control? And would NFC provide incremental validity in predicting burnout?
“adults” in which context?

@@

\RC{Page 4

@@

>>>>

[address frist sentence] We deleted the reference to Grass et al. because referencing it in full would have exceeded the word limit for the abstract.

@@

We rewrote the respective sentences as the phrasing obviously was misleading. The respective sentences now read:

> "with these associations being in a small to medium range."

> "... because the worker is often in conflict ..."

\RC{Page 3. 
How is NFC related to other constructs like neuroticism, self-esteem, and locus of control? And would NFC provide incremental validity in predicting burnout?

“adults” in which context?

@@

\Assignment{JZ}
# Comment: see Table 2 in Fleischhauer et al. (2019)

\RC{Page 4.

@@

We are aware that the double-blind review process somewhat interferes with Open Science issues. We learned how OSF projects can be anonymized only after submission of our manuscript. We apologize that we did not give the reviewer the opportunity to check our preregistration/data/code. Of course, we share our data and code openly on OSF and also provide a license for re-use (CC-4.0-BY).
